GeoSched: Minimizing Cost of Cloud Workloads in Geo-Distributed Data Centers

### 2015-03-14 doc/report/survey/article.tex
google workload code + project files

 \subsection{Study real-time and synthetic workloads} We have started studying workloads traces for google cluster-data which provides traces from a 12k-machine cell for one month duration in May 2011. This process is challenging because task-IDs, job-IDs are obfuscated for security reasons. Resources utilization such as CPU and memory has been normalized with the maximum resource usage. We are also studying synthetic workloads that are generated by sampling historical MapReduce cluster traces. Tentatively we would complete this by 10\textsuperscript{th}March,2015.
 \subsection{Data Center profile}In this process we will note the data center specific parameters such as electricity cost, available energy, economizer, cooling energy that is useful for simulating geo-replicated data centers.We would complete this by 20\textsuperscript{th}March,2015.
\subsection{Feature Extraction} This phase will be identifying all the necessary features that contribute to the energy cost. These features will be used in the optimization of the energy cost. We aim to complete this by 5\textsuperscript{th}April,2015.
 \subsection{Implementing Optimization technique} This is the most critical component and expected to consume major part of project. We will be building optimization techniques which is adaptive to workload characteristics and data center's resource capacity and electricity costs.We aim to complete this by 25\textsuperscript{th}April,2015.
\subsection{Evaluation} This phase we will be simulating data centers with previously gathered data center profile and using the optimization technique mentioned above.We aim to complete this by 7\textsuperscript{th}May,2015.

>>>>

 \subsection{Study real-world and synthetic workloads} We have started studying workloads traces for google cluster-data which provides traces from a 12k-machine cell for one month duration in May 2011. This process is challenging because task-IDs, job-IDs are obfuscated for security reasons. Resources utilization such as CPU and memory has been normalized with the maximum resource usage. We are also studying synthetic workloads that are generated by sampling historical MapReduce cluster traces. Tentatively we would complete this by 10\textsuperscript{th}March,2015.
 \subsection{Data Center profile}In this process we will note the data center specific parameters such as electricity cost, available energy, economizer, cooling energy that is useful for simulating geo-replicated data centers.We would complete this by 20\textsuperscript{th}March,2015.
\subsection{Feature Extraction} This phase will be identifying all the necessary features that contribute to the energy cost. These features will be used in the optimization of the energy cost. We aim to complete this by 5\textsuperscript{th}April,2015.
 \subsection{Implementing Optimization technique} This is the most critical component and expected to consume major part of project. We will be building optimization techniques which is adaptive to workload characteristics and data center's resource capacity and electricity costs.We aim to complete this by 25\textsuperscript{th}April,2015.
\subsection{Evaluation} This phase we will be simulating data centers with previously gathered data center profile and using the optimization technique mentioned above.We aim to complete this by 7\textsuperscript{th}May,2015.
